Computer Science House By-Laws

### 2016-06-19 bylaws.tex
Removing Housing evals

\bsubsection{Housing Evaluation}
The Housing Evaluation process occurs during the academic year.
It is performed late Spring Semester before or concurrently with the Membership Evaluation and is chaired by the Evaluations Director.
The Housing Evaluation is used to recognize an individual’s contributions to the House and distribute Housing Points (see \ref{Housing Priority System}).
All Active members who wish to be evaluated are required to submit an activity report in which they may log projects worked on, social events and seminars hosted or attended, and any other information they deem relevant.
A member’s failure to submit the activity report will result in that member receiving no housing points.
Attendance is also required for a member to be evaluated, else they will receive no housing points.
Any member unable to attend because of outstanding circumstances (e.g. away on co-op) may also submit an activity report and be voted on, though they may not vote.
Members in this situation should contact the Evaluations Director at least one day prior to the evaluation.
The participating members, on a member by member basis, review the activity report provided by each member.
The participating members may then choose to award one, two, or three housing points to each member.
Points are awarded on the basis of contributions to House.
Above average members receive three points, average members two points, and below average members one point.
A quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
Neither Absentee nor Proxy votes are allowed.

>>>>

\bsubsection{Housing Points}
All members may notify the evaluations director before the end of the academic year that they would like to receive two housing points for use in the next academic year.
